\documentclass[]{resume-openfont}
\usepackage{fancyhdr}
 \usepackage{pdfpages}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Hasan Ali}{Khattak}{ \urlstyle{same}\href{mailto:hasan.alikhattak@gmail.com}{hasan.alikhattak@gmail.com} | +92123456789 | \href{http://hasan.khattak.info}{hasan.khattak.info} | \href{https://orcid.org/0000-0002-8198-9265/print}{ORCID: 0000-0002-8198-9265}\\
Asst. Prof. Computer Science, COMSATS University Islamabad, Pak - PhD. Computer Engineering - Italy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Politecnico di Bari}
\descript{PhD Electrical and Computer Engineering}
\location{April 2015 | Bari, Italy}
\location{Architectures for the Semantic \\Web of Things}
\sectionsep

\subsection{Politecnico di Torino}
\descript{MS in Control and Computer Engineering}
\location{December 2011 | Torino, Italy}
\location{ Grade: 26 / 30}
\sectionsep

\subsection{NUST SEECS}
\descript{MS in Information Technology}
\location{October 2009 | Islamabad Pakistan}
\location{ Cum. GPA: 3.02 / 4.0}
\sectionsep

\subsection{University of Peshawar}
\descript{BS in Computer Science}
\location{April 2007 | Peshawar, Pakistan}
\location{ Cum. GPA: 3.4 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Google Scholar:// \href{https://scholar.google.com.pk/citations?user=dyEt0FUAAAAJ&hl=en}{\bf Hasan Ali Khattak}
LinkedIn://  \href{https://www.linkedin.com/in/hasanalikhattak}{\bf hasanalikhattak} \\
Github:// \href{https://github.com/hasanalikhattak}{\bf hasanalikhattak} \\
Twitter://  \href{https://twitter.com/hasanalikhattak}{\bf @hasanalikhattak} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Teaching}
\subsection{Graduate}
Advanced Object Oriented Software Engineering \\
Advanced Distributed Computing\\
Software Engineering for Healthcare \\
Advanced Topics in Networks (IoT)\\
\sectionsep

\subsection{Undergraduate}
Web Engineering \\
Operating Systems \\
Artificial Intelligence \\
Objection Oriented Programming \\
Scripting Languages\\
Computer Ethics \\
{\footnotesize \textit{\textbf{(Professional Practices in IT)}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{} Shell \textbullet{} Python \textbullet{} Javascript \textbullet{} Matlab \textbullet{} Rails \textbullet{} \LaTeX \\
\location{Familiar:}
PhP \textbullet{} Android \textbullet{} MySQL \textbullet{} C/C++  \textbullet{} Tk/Tcl
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{COMSATS University Islamabad}
\descript{| Assistant Professor }
\location{January 2016 - Present | Islamabad, Pakistan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Leading Information Systems Research Group.
\item Successfully supervised 5+ Graduate and 40+ Under-graduate students. 
\item Completed 3 Funded Projects. 
\end{tightemize}
\sectionsep

\runsubsection{Politecnico di Bari}
\descript{| Post Doc Researcher | SisInf Lab PoliBa}
\location{Jan 2015 – December 2015 | Bari, Italy}
\vspace{\topsep}
\begin{tightemize}
\item Semantic Web of Things based Healthcare Monitoring for Old Age Patients.
\item Co-Supervising Graduate and Under-grad Students.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Portfolio}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Selected Publications - Impact Factor 82.071}
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{resume-openfont}
\nocite{*}
\sectionsep

\runsubsection{Funded Projects}\\
\descript{Principal Investigator}
\location{Higher Education Commission, Pakistan (Islamabad, Pakistan) | GRANT 1122}
Smart Patient Monitoring for elderly.  

\location{Higher Education Commission, Pakistan (Islamabad, Pakistan) | GRANT 1674}
Commercial Southbound API security for SDN.  
\sectionsep

\descript{Co-Principal Investigator}
\location{Higher Education Commission, Pakistan (Islamabad, Pakistan) | GRANT 1115}
Semantic Researcher Repository.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Services
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Professional Services}
\descript{Reviewer}
IEEE Consumer Electronics Magazine, Eurasip Journal on Wireless Communications and Networking, IEEE Access, Journal of Experimental and Theoretical Artificial Intelligence, Journal of Information Science\\
\descript{Editorial}
EURASIP Journal on Wireless Communications and Networking, Hindawi Wireless Communications and Mobile Computing
\end{minipage}
\end{document}